%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% !TeX spellcheck = en_US

%% Uses same structure as the resume. Modified for Cover Letter - wherever required.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%			PAGE CONFIGURATIONS & Packages		 %%%
%%%	NOTE: Check PackageConfig.tex for More Info. %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt, a4paper]{article}

\usepackage{lmodern}
\usepackage{fontspec}
\usepackage{lettrine}            % First Letter of Large Size is called as lettrine
\usepackage{multicol}            % Package for Easy Rendering of Multiple Columns
\usepackage{graphicx}
\usepackage[none]{hyphenat}      % Usage \nohyphens{<long-length-word>}
\usepackage{geometry}            % Package for Defining Margin
\usepackage{fancyhdr}            % Using fancyhdr for Header & Footer Control
\usepackage{blindtext}           % for generating Lorem-Ipsum Dummy Text
\usepackage{fontawesome}         % Package for Icons from Font-Awesome
% \usepackage{draftwatermark}      % Watermark as DRAFT/CONFIDENTIAL/etc.

\usepackage[super]{nth}          % for Writing 1\textsubscript{st}, 2\textsubscript{nd} etc.
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}  % Text (Custom) Colors
\usepackage[hidelinks]{hyperref} % DONOT Highlight URLs (remove optional Argumemnts?)

\input{"./PackageConfig.tex"}    % Inserting all Package Configurations
\input{"./AuthorDetails.tex"}    % Inserting Author Details Informations
\input{"./information-coverletter.tex"} % Include other information for cover letter

%%% --- MAIN DOCUMENT --- %%%

\setlength{\parindent}{0em}

\begin{document}
	\begin{center}
		\textcolor{dBlue}{{\HeaderNFont \AuthorFName}\hspace{0.7cm}{\HeaderNFont \AuthorLName}} \\
		\vspace{2pt}
		{\small \textcolor{dBlue}{\CyberPresence}}
		\vspace{-23pt}
	\end{center}

	\textcolor{dBlue}{
		\\ \noindent\makebox[\linewidth]{\rule{\textwidth}{2.1pt}}
		\vspace{-21pt} \\
		\noindent\makebox[\linewidth]{\rule{\paperwidth}{3.9pt}}
		\vspace{-13pt} \\
	}

	%%% --- Cover Letter --- %%%
	 \addressee{Whom it May Concern}{Gurgaon, India}
%	\addressee{Prof. XYZ}{Name of the Place}

	%%% --- >>> START : LETTER FOR PhD. APPLICATION <<< --- %%%
	% POINTS/NOTES that can be included into the PhD Application
	% 1. Advantage of considering my canditure for PhD as I have an industry experience, and how it will help in efficient system
	%%% --- >>> END : LETTER FOR PhD. APPLICATION <<< --- %%%

	%%% --- >>> START : GENERAL LETTER STRUCTURE FOR JOB OPPORTUNITY <<< --- %%%
	% \begin{flushleft}
	I have completed my \textit{graduations} from Neotia Institute of Technology Management and Science under the Maulana Abul Kalam Azad University of Technology (formerly West Bengal University of Technology, WBUT) majoring \textit{in Electrical and Electronics Engineering}. \\[3pt]

	I'm currently working at Reliance Industries as a Data Analyst since October 2016, and have \textbf{6.5+ years of experience} in developing \textit{end-to-end \textbf{machine learning and deep learning solutions using python}}. In addition, I have \textbf{2+ years of team building experience} wherein I guide and develop \textit{production ready} robust codes. \\[3pt]

	I take advantage of the \textbf{Data Science and Analyst Team in Reliance Industries}, wherein close guidance, I devise Rule-Based Algorithms together with Analytic-Driven, Data-Wrangling Methodologies which facilitate my responsibilities for building Business Logics which is not only restricted to saving operational costs, improving speed and accuracy of the system and enhancing customer-experience quality. \\[3pt]

	Along with my professional expertise, I have completed my \textit{masters in Power Electronics and Electrical Drives from \textbf{Indian Institute of Technology} (IIT-ISM)}, Dhanbad, which gave me a strong foothold to devise optimized solutions, and carry out tasks assigned to me. \\[3pt]

    % My academic experience gave me an opportunity to work with power market data like prediction of MCV \& MCP for DAM and RTM Indian Market. In addition, I have published a paper on IEEE titled ``Reliable Estimation of Dissipation Factor for In-Servie Power Transformers''. Thus, I believe, I am a perfect fit for this job role, given \textbf{6+ years of relevant industry experience} along with expertise in \textbf{energy sector}. \\[3pt]

    My academic experience, along with my professional expertise gives me an unique advantage of robust optimization and analytical thinking abilities, along with the ability of learning things quickly. My resume indicates that I’m a hardworking, goal-oriented person who is well equipped to work in a group and/or individually. I’m responsible enough and can complete an assigned task on time. I thus would like you to consider my resume along with it. \\[3pt]

	I believe I am a perfect fit for this role as I not only have relevant experience but also have leadership skills where me and my team have delivered exceptional results like network optimization automation and enhancing business growth by deploying production tools to automate and reduce manpower! \\[3pt]

	With the aforesaid qualities and expertise of mine, I am confident that I can offer you the skills that you are seeking. I would like to consider myself for a personal interview at your convenience. \\[3pt]

	Your kind and a valuable reply are highly appreciated. \\[3pt]

	Wish the letter reaches you in Good Health. \\[5pt]

	Regards, \\ \AuthorFullName

    %\pagebreak
    %\input{"./AdditionalDetails.tex"}
	% \end{flushleft}
	%%% --- >>> END: GENERAL LETTER STRUCTURE FOR JOB OPPORTUNITY <<< --- %%%
\end{document}