%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%------------------------------------------------%
%	File Information : Work Experience Template
%
%	Import using \input{"./sections/publications.tex"}
%	NOTE: Commands are Defined in main.tex
%------------------------------------------------%

\SectionName{Research \& Publications}

\SubHeaders{\ExtLink{https://app.box.com/s/2dn62qwp868cuxc021rvu3k1z3lydsgd}{Designing a Finger Based Heart Rate Monitoring System and Creating a Service Application for Data Transfer and Visualization using LABView Simulation Toolkit}}{Neotia Institute of Technology Management and Science}{\textit{Final Year Project}}{Diamond Harbor, West Bengal (India)} \\
Took as a part of Final Year Project under the guidance of \ExtLink{https://scholar.google.com/citations?user=sfx25tQAAAAJ&hl=en}{Dr. Pulak Pattanayak} (Asst. Prof. Dept. of Electrical and Electronics Engineering, NITMAS, and H.O.D. of Physics, NITMAS). A brief working summary and the responsibilities of the project is as follows:
\begin{itemize}
	\item Building a hardware using photodiode and infrared sensor which can detect the heart rate of a person – the sensor is carefully placed in a person’s finger from where the heart rate is to be monitored.
	\item Getting the output of the Heart Rate from the hardware and displaying the pulse in CRO.
\end{itemize}
\textbf{Project Partners :} \ExtLink{https://www.linkedin.com/in/jishnu-bhattacharyya-8b7793b7/}{Jishnu Bhattacharyya}, Mainak Ghosh, Priti Kumari

\SubHeaders{\ExtLink{https://www.researchgate.net/publication/342571393_Layer_Wise_Segmentation_in_Skin_OCT_Using_Random_Walks_REPORT}{Layer wise Image Segmentation of Skin OCT using Random Walks}}{Indian Institute of Technology (IIT)}{\nth{15} June - \nth{14} July, 2015}{Kharagpur, West Bengal (India)} \\
Took as a part of Summer Internship under the guidance of \ExtLink{http://www.facweb.iitkgp.ac.in/~debdoot/}{Dr. Debdoot Sheet} (Asst. Prof. Dept. of Electrical Engineering, IITK). The project was to Build a Simulation Code to Detect the Layers of Skin (dermis) from an OCT Image using MatLAB (Image Processing Library).

\section*{Others}
\begin{itemize}
	\item \ExtLink{https://app.box.com/s/ld1671zzpvswjchnszpgdqzoxfss9yj6}{Inverter Design Methodology and Efficiency of Solar PV Systems}
	\item \ExtLink{https://www.researchgate.net/publication/312071041_Experiment_Series_and_Parallel_Combination_of_PV_Modules_At_Indian_Institute_of_Engineering_Science_Technology_Shibpur}{Series and Parallel Combination of PV Modules}
\end{itemize}