%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%------------------------------------------------%
%	File Information : Work Experience Template
%
%	Import using \input{"./sections/skills.tex"}
%	NOTE: Commands are Defined in main.tex
%------------------------------------------------%

\SectionName{Skills}



\begin{multicols}{2}
	\SkillsHeaders{Core Skills in Data Science \& Analytic}
	\begin{itemize}
		\item Python (pandas, NumPy, Scikit-Learn, SciPy)
		\item Statistics Analysis and Data Interpretation
		\item Machine Learning Algorithms – Regression, Clustering, PCA, K-Means, KNN, Decision Trees, Random Forest, XGBoost
		\item Neural Networks – Primitive Networks (MP Neuron, Hebb’s Network, Perceptron), Back Propagation Algorithms; and Deep Neural Network - Design and Modeling (using Keras with TensorFlow); RL with Self Organizing Maps (SOM)
		\item Optimization Methodologies – Linear Programming (or Simplex Algorithm), Single or Multi-Variable Optimizations, Multi-Objective Optimization Techniques
		\item \nohyphens{Specialized Methodologies like Genetic Algorithms (GA), Multi-Objective Genetic Algorithm, Particle Swarm Optimization (PSO), Ant-Colony Optimization (ACO), Gradient Descent}
		\item Databases : Apache Hive; MongoDB (\textit{basic}); SQL (MySQL, Google Big-Query, Postgre-SQL (PSQL))
		\item Data Visualization Tools: Tableau, PowerBI
        \item Machine Learning Frameworks: TensorFlow (v2.0+) with Keras (backend), PyTorch
        \item Automation Tools: CI/CD Pipelines, GIT
		\item \textbf{Data Engineering Skills:} \textit{(basics)} MLOPs, DVC, ML Model Deployment and Monitoring
	\end{itemize}

	\SkillsHeaders{Electrical and Computer Science Engineering}
	\begin{itemize}
		\item Web Frameworks for building REST API using Flask.
		\item Virtualization of Application as Service using Docker.
		\item Hadoop and Big Data for Handling Large Data and Running Analysis.
		\item MatLAB \& Simulink (Mathematics, Control System \& Image Processing Toolbox).
		\item Mathematical Modelling of Control Systems.
		\item Simulation Software: MultiSIM, PSIM.
        \item Power Market - DAM, RTM, GDAM, GTAM, etc. and Scheduling of Power in NLDC/IEX. Demand forecasting, MCP/MCV forecasting.
        \item Power Transformers \textit{(basics)} - insulation and condition based monitoring techniques.
	\end{itemize}
\end{multicols}